Interpreting Random Forest Predictions for Firearm Identification Using LIME

### 2018-11-28 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
updated seeds

  # Create the data (with a set seed)
  set.seed(1837592)
  hamby173and252_train_sub <- hamby173and252_train %>%
    filter(samesource == FALSE) %>%
    slice(sample(1:length(hamby173and252_train$barrel1), 4500, replace = FALSE)) %>%
    bind_rows(hamby173and252_train %>% filter(samesource == TRUE))

>>>>

  # Create the data (with a set seed)
  set.seed(20181128)
  hamby173and252_train_sub <- hamby173and252_train %>%
    filter(samesource == FALSE) %>%
    slice(sample(1:length(hamby173and252_train$barrel1), 4500, replace = FALSE)) %>%
    bind_rows(hamby173and252_train %>% filter(samesource == TRUE))
